Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Community Detection and Parameter Estimation

### 2021-03-09 summary.Rmd
more cleanup

Using results from \citet{soltanolkotabi2012}, it can be easily shown that 
the SSC detection property holds for $XU$, which is an ASE of $P$. More 
specifically, if points lie exactly on mutually orthogonal subspaces, then the 
SSC detection property will hold with probability 1, and this is exactly the 
case for the PABM (Theorem 2). Much of our work is then built on \citet{ribindelanchy2017statistical}, who describe the convergence behavior of 
the ASE of $A$ to the ASE of $P$, and \citet{pmlr-v28-wang13}, who show the 
necessary conditions for the SSC detection property to hold in noisy cases 
where the points lie near subspaces.

>>>>

Using results from \citet{soltanolkotabi2012}, it can be easily shown that 
the SSC detection property holds for $XU$, which is an ASE of $P$. More 
specifically, if points lie exactly on mutually orthogonal subspaces, then the 
SSC detection property will hold with probability 1, and this is exactly the 
case for the PABM (Theorem 2). Much of our work is then built on \citet{rubindelanchy2017statistical}, who describe the convergence behavior of 
the ASE of $A$ to the ASE of $P$, and \citet{pmlr-v28-wang13}, who show the 
necessary conditions for the SSC detection property to hold in noisy cases 
where the points lie near subspaces.
